Title: A proof-of-concept study

### 2022-01-07 paper.tex
update

  \begin{figure}
    \includegraphics[width=\columnwidth]{figures/fig__jetI5+ismSeed3-45deg_no-disk-stratified-ambient-Pres-Dens-Temp.png}
    \caption{Comparison of the cases with (left) and without (right) the dense disk.\
             In the both cases, the bipolar jets are injected at the origin along the $z=-y$ direction\
             with a constant 4-velocity of 0.6 for a duration of 1.2 Myr.
             The pressure (top), temperature (middle), and number density (bottom) slices\
             through the jet sources show that the dense disk not only helps the bubbles to align the disk normal\
             but also creates an under pressure, cold, and dense bubble in the most inner region.
             }
    \label{fig__jetI5+ismSeed3-45deg_no-disk-stratified-ambient-Pres-Dens-Temp}
  \end{figure}

>>>>

  \begin{figure*}
    \includegraphics[width=\linewidth]{figures/fig__jetI5+ismSeed3-45deg_no-disk-stratified-ambient-Pres-Dens-Temp.png}
    \caption{
             Comparison between the case with the clumpy (the first column from the left)\
             and smooth disk (the second) in the stratified atmosphere\
             shows that the density distribution of the dense disk has insignificant effect\
             on the overall dynamics of the bubbles. However, the bubbles with the smooth disk (the third)\
             in a uniform atmosphere is spherical-shape,\
             suggesting the stratified ambient helps to elongate bubbles notably.\
             Moreover, the rightmost column shows that the bubbles without the disk is tilted even\
             in the stratified atmosphere, indicating the dense disk is a crucial component\
             for the formation of axis-symmetric bubbles.\
             In all the cases, the bipolar jets are injected at the origin along the $z=-y$ direction\
             with a constant 4-velocity of 0.6 for a duration of 1.2 Myr.
             The pressure (top), temperature (middle), and number density (bottom) slices\
             through the jet sources show that the dense disk not only helps the bubbles to align the disk normal\
             but also creates an under pressure, cold, and dense bubble in the most inner region.
             % , undetected by any telescopes (frame the inner bubble)
             }
    \label{fig__jetI5+ismSeed3-45deg_no-disk-stratified-ambient-Pres-Dens-Temp}
  \end{figure*}
